---
title: "Greg Chism's CV"
author: Greg Chism
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
  cache_data:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("CV_printing_functions.R")

# Read in all data and initialize a CV printer object
# CV <- create_CV_object(
#   data_location = "https://docs.google.com/spreadsheets/d/1JeUL4uGOdpvpGP2jDXWQuHL-IpTdDztiWxSP4qavlKE/edit#gid=917338460",  
#   pdf_mode = params$pdf_mode,
#   cache_data = params$cache_data
# )

CV <- readr::read_rds('cached_positions.rds')

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r}
if(params$pdf_mode){
  cat("View this CV online with links at https://gregtchism.netlify.app/cv/gchism_cv.pdf/")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/Gchism94/cv/raw/master/gchism_cv.pdf)")
}
```

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```



Relevant Skills {#skills}
--------------------------------------------------------------------------------

**Programming/Software**

- R/RStudio
- R Markdown/Quarto
- Git/GitHub
- Shiny
- Python
- Bash
- Docker 
- CyVerse
- OpenRefine
- HTML/CSS/SCSS
- Mathematica
- Microsoft Office Suite
- Netlogo/Agent-Based Models

**Data Science**

- Data Visualization 
- Biostatistics
- Open Science
- Computational Thinking
- Containers
- Biological Modeling
- Image/Video Analysis
- Website Design 


 

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with [**pagedown**](https://github.com/rstudio/pagedown): 
[Source code](https://github.com/Gchism94/cv).

Last updated on `r Sys.Date()`.



Main
================================================================================

Greg Chism {#title}
--------------------------------------------------------------------------------

***


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('Education')
```

Certifications {data-icon=certificate}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('Certifications')
```


Related Work Experience {data-icon=briefcase}
--------------------------------------------------------------------------------


```{r}
CV %<>% print_section('Relavant_Work_Experience')
```


Teaching and Mentorship {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------


```{r}
CV %<>% print_section('Teaching_and_Mentorship')
```



Professional Development {data-icon=user-tie}
--------------------------------------------------------------------------------


```{r}
CV %<>% print_section('Professional_Development')
```


Published Teaching Curriculum {data-icon=book-open} 
--------------------------------------------------------------------------------


```{r}
CV %<>% print_section('Published_Curriculum')
```


<i class="fab fa-jedi-order"></i> Published Research Compendium  
--------------------------------------------------------------------------------


```{r}
CV %<>% print_section('Published_Compendium')
```



Published Research {data-icon=book}
--------------------------------------------------------------------------------


```{r}
CV %<>% print_section('Publications')
```


Published Datasets {data-icon=database}
--------------------------------------------------------------------------------


```{r}
CV %<>% print_section('Published_Datasets')
```


Outreach and Service {data-icon=handshake}
--------------------------------------------------------------------------------


```{r}
CV %<>% print_section('Outreach_Service')
```


<i class="fas fa-chalkboard"></i> Invited Talks 
--------------------------------------------------------------------------------


```{r}
CV %<>% print_section('Invited_Talks')
```


Selected Awards {data-icon=money-bill}
--------------------------------------------------------------------------------


```{r}
CV %<>% print_section('Fellowships_Awards')
```


References 
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('References')
```
